How to be a good member of a scientific software community [Article v\versionnumber]

### 2021-08-17 paper.tex
more text

    \item Give the version of the code you're using.

@@

Sometimes, the developer will be able to answer your question based on the first
email. However, their reply will often contain questions or suggestions for
things to test. \emph{It is crucial that you read this message carefully, and
answer all of the questions to the best of your ability when you reply.} As a
rule, these questions aren't asked idly; the person providing support is trying
to help you! Far too often, users don't read the reply email carefully, don't
answer the questions, try only the first suggestion, or refuse to indicate what
it is they were actually doing. If you do this, the best case is that it will
take longer for you to get to a solution. More likely, you will frustrate the
person trying to help you, and they may become reluctant to work on your issue.

@@

@@

\begin{checklist}{A good community}
\begin{itemize}
\item Helps users solve their problems
\item Is friendly and supportive when responding to questions
\item Is receptive to suggestions and critiques, regardless of the source
\item Encourages participation from users of all experience levels
\item Encourages respectful treatment of all community members, and calls out disrespectful behavior
\end{itemize}
\end{checklist}

@@

Alan Grossfield serves as a consultant to two companies, Moderna, Inc.
and Atelerix Life Sciences.

>>>>

    \item Give the version of the code you're using. If you've changed anything,
    say what you've changed. If there are compile-time options, say what you
    chose.

@@

Sometimes, the developer will be able to answer your question based on the first
email. However, their reply will often contain questions or suggestions for
things to test. \emph{It is crucial that you read this message carefully, and
answer all of the questions to the best of your ability when you reply.} As a
rule, these questions aren't asked idly; the person providing support is trying
to help you! Far too often, users don't read the reply email carefully, don't
answer the questions, try only the first suggestion, or refuse to indicate what
it is they were actually doing. If you do this, the best case is that it will
take longer for you to get to a solution. More likely, you will frustrate the
person trying to help you, and they may become reluctant to work on your issue.
In my experience, few things are more frustrating than trying to help someone
who won't help me help them.

@@

Once you've become reasonably competent with a piece of software, it's worth
looking for ways to contribute back. This can take many forms, not all of which
involve writing code (though of course contributing bug fixes or new features is
extremely valuable). You can work on the documentation --- if you struggled to
understand something but eventually figured it out, consider contributing a new
paragraph of text; many packages hosted on GitHub have the documentation in the
same repository, so the same pull request mechanism can be used, but even if the
docs are separate you could write a new paragraph or two and send them to the
developer. If you developed a toy example as you were figuring out how to use
the software, consider sharing it. If one of the provided examples had to be
tweaked to work, share the tweaks. If the software has an online forum (e.g.
mailing list, GitHub discussions or issues, etc), you might be able to
contribute by suggestion solutions to problems from less experienced users. However, unlike the other recommentations, this one isn't mandatory --- it's a ``nice to have'' rather than a ``must have''.

@@

\begin{checklist}{A good community}
\begin{itemize}
\item Helps users solve their problems
\item Is friendly and supportive when responding to questions
\item Is receptive to suggestions and critiques, regardless of the source
\item Encourages participation from users of all experience levels
\item Encourages respectful treatment of all community members, and calls out bad behavior
\end{itemize}
\end{checklist}

@@

Alan Grossfield serves as a consultant to two companies: Moderna, Inc.
and Atelerix Life Sciences.
